Spike-in_MSstatsPTM_Analysis

### 2022-03-05 code/Spike-in_Analysis.Rmd
experimental design changes

```{r pressure, echo=FALSE, fig.width = 10, fig.height = 7}
load(file = "../data/Spike_in_MSstatsPTM_Model.rda")#model_df

>>>>

```{r pressure, echo=FALSE, fig.width = 10, fig.height = 7}
load(file = "D:\\Northeastern\\Research\\MSstats\\PTM_Refractor\\Label_Free_PTM_Data\\benchmark-spike\\MSstatsPTM_Summarized.rda")

summary_df$PTM$RunlevelData

load(file = "../data/Spike_in_MSstatsPTM_Model.rda")#model_df
